---
title: "Burden or Builders? (Replication Package)"
authors: "Sepehr Ekbatani, Mohammad Mostafawi"
date: "`r Sys.Date()`"
output:
    html_document:
        theme: readable    
        highlight: kate
        toc: true    
        toc_depth: 4
        toc_float: true    
        df_print: kable
        code_folding: hide    
        css: styles.css
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
# Set global options
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)


```

```{r,include=FALSE}
library("RODBC")
library("tibble")
library("dplyr")
library("ggplot2")
library("reshape2")
library("sf")
library("shiny")
library("leaflet")
library("kableExtra")
library("knitr")
library("data.table")  
library("tidyr")
library("haven")
library("purrr")
library("stringr")
library("readxl")
library("readr")
library("broom")
library("AER")
library("sandwich")
library("lmtest")
library("fixest")
library("dplyr")
library("purrr")
library("writexl") 
library("readxl")
library("xtable")
library("stargazer")
library("multiwayvcov")
library("survey")
library("htmltools")
```


# Demand Side Analysis

## Importing and Basic Cleanings

```{r, message=FALSE}
##  Import HEIS + basic recodes
## =========================

expenditure_all <- read_dta("HEIS.dta")

expenditure_all <- expenditure_all %>%
  mutate(
    # Make sure marital status is numeric, then collapse 2/3/4 into 0 (non-category-1)
    Marital_Status_HH_Head = as.numeric(Marital_Status_HH_Head),
    Marital_Status_HH_Head = ifelse(Marital_Status_HH_Head %in% c(2, 3, 4),
                                    0,
                                    Marital_Status_HH_Head)
  )

# Log of main expenditure aggregates (add 1 to handle zeros)
expenditure_all$log_housing       <- log(expenditure_all$housing       + 1)
expenditure_all$log_food          <- log(expenditure_all$food          + 1)
expenditure_all$log_durables      <- log(expenditure_all$durables      + 1)
expenditure_all$log_education     <- log(expenditure_all$education     + 1)
expenditure_all$log_transportation<- log(expenditure_all$transportation+ 1)


## =========================
## Province-level controls and population
## =========================

all_populations <- read_dta("LFS.dta")

# Harmonise province codes across files
expenditure_all <- expenditure_all %>%
  mutate(province = as.numeric(province))


all_populations <- all_populations %>%
  mutate(
    province = as.numeric(province),
    year     = as.numeric(year)
  )
# Important note: There are two columns of years in this data: "Year" and "year"
# "Year" is in Gregorian Calendar and "year" is in Persian Solar Calendar
# "Year" is from 2018 to 2023 and "year" is from 1397 to 1402 in Persian Calendar



## =========================
## Clean population file and merge
## =========================

# Align province name to match other files
all_populations <- all_populations %>%
  rename(Province = province_name)

# Fix mixed coding of Persian year (e.g. 99 → 1399, 400 → 1400)
all_populations <- all_populations %>%
  mutate(
    year = case_when(
      year < 100                   ~ 1300 + year,        # e.g. 99  → 1399
      year >= 400 & year < 500     ~ 1000 + year,        # e.g. 400 → 1400
      TRUE                         ~ year
    )
  )

# Rename the dataset of HEIS
consumption <- expenditure_all
# Add population data to the main file
consumption <- consumption %>%
  left_join(all_populations, by = c("province", "Province", "year"))


## =========================
## Night-time lights, land area, and population density
## =========================

# NTL data at province-year level
Iran_ntl <- read_csv("Iran_ntl.csv")

# Merge NTL into the main file (keys must match how they are stored in the raw files)
consumption <- consumption %>%
  left_join(Iran_ntl, by = c("Province", "Year"))

# Province land area (km²)
iran_province_areas <- read_csv("Iran_province_areas.csv")

consumption <- consumption %>%
  left_join(iran_province_areas, by = "Province") %>%
  mutate(
    # Population density: total population per km²
    pop_density = total_pop / Area_km2
  )





```


## Summary Stats
### Table 1: consumption Summary stat 

```{r}
## ==================================================
## Summary statistics: consumption data (analysis sample)
## ==================================================

# Reconstruct total consumption (replace old total)
consumption <- consumption %>% 
  mutate(
    total = food +
            catering_food +
            housing +
            education +
            transportation +
            communication +
            durables +
            health,
    
    # log(total + 1) to avoid log(0) cases
    log_total = log(total + 1)
  )

# Fix miscoded income earners and numeric issues
consumption <- consumption %>%
  mutate(
    Num_Income_Earners = ifelse(Num_Income_Earners == 99, 0, Num_Income_Earners),
    nroom = as.numeric(as.character(nroom)),
    floor = as.numeric(as.character(floor))
  )

# Variables for the table (same as before, but log_total updated)
vars_summ <- c(
  "log_housing","log_total","log_food",
  "log_durables","log_education","log_transportation",
  "nroom","floor",
  "afghan_pct",
  "Num_HH_Members","Num_Male","Num_Under14",
  "Num_Over65","Num_Income_Earners",
  "ntl","pop_density"
)
vars_summ <- intersect(vars_summ, names(consumption))


# Analysis sample
cons_sample <- consumption %>%
  filter(year %in% 1397:1402) %>%
  filter(complete.cases(across(all_of(c(vars_summ, "weight")))))


# Weighted summary function
summ_fun_w <- function(x, w) {
  x <- as.numeric(x)
  w <- as.numeric(w)

  w <- w / sum(w)  # normalize

  # weighted percentiles
  ord <- order(x)
  x_sorted <- x[ord]
  w_sorted <- w[ord]
  cum_w <- cumsum(w_sorted)

  w_quant <- function(p) x_sorted[which(cum_w >= p)[1]]

  c(
    N    = length(x),
    mean = sum(w * x),
    sd   = sqrt(sum(w * (x - sum(w * x))^2)),
    min  = min(x),
    p25  = w_quant(0.25),
    p50  = w_quant(0.50),
    p75  = w_quant(0.75),
    max  = max(x)
  )
}

# Build weighted summary table
cons_summary_table <- t(
  sapply(vars_summ, function(v)
    summ_fun_w(cons_sample[[v]], cons_sample$weight)
  )
)

cons_summary_table <- as.data.frame(cons_summary_table)
rownames(cons_summary_table) <- vars_summ

# Show in R
print(round(cons_summary_table, 3))

# Export to LaTeX
cons_summary_tex <- capture.output(
  stargazer(
    cons_summary_table,
    type = "latex",
    summary  = FALSE,
    header   = FALSE,
    rownames = TRUE,
    title = "Weighted summary statistics: household consumption sample",
    label = "tab:summary_consumption",
    digits = 3
  )
)

cat(cons_summary_tex, sep = "\n",
    file = "table_summary_consumption.tex")


```






### Table 3: IV-DiD (Main Analysis)

### Two IV's, Banned and afghan_share96 which shows the percentage of afghans in each province from total afghans in year 1996 



```{r}
## ==================================================
##  Baseline DiD (no IV) and IV–DiD (two IVs)
##    + export to LaTeX as Table 1 (Panel A/B)
## ==================================================

consumption <- consumption %>%
  filter(year %in% 1397:1402) %>%
  filter(complete.cases(across(all_of(c(vars_summ, "weight")))))



##  Construct afghan_share96 (province share of total Afghans in 1996)
consumption <- consumption %>%
  group_by(Province) %>%
  mutate(
    # Provincial Afghan count in 1996 (same within province)
    Afghans_prov = first(Afghans)
  ) %>%
  ungroup() %>%
  mutate(
    # Total Afghan population in 1996 across provinces
    total_Afghans_1996 = sum(Afghans_prov, na.rm = TRUE),
    # Province share of national Afghan total
    afghan_share96      = Afghans_prov / total_Afghans_1996
  ) %>%
  select(-Afghans_prov, -total_Afghans_1996)


##  Define banned provinces (for second IV)
forbidden_provinces <- c(
  "East Azerbaijan","West Azerbaijan","Ardabil","Zanjan",
  "Kurdistan","Kermanshah","Ilam","Chaharmahal and Bakhtiari",
  "Kohgiluyeh and Boyer-Ahmad","North Khorasan","Gilan",
  "Mazandaran","Sistan and Baluchestan","Khuzestan",
  "Hamadan","Lorestan"
)

# List of controls (Year and Province included for FE)
ctrls <- c(
  "ur","Num_HH_Members","Num_Male",
  "Num_Under14","Num_Over65",
  "Education_Level_HH_Head","Marital_Status_HH_Head",
  "ntl","pop_density","Year","Province"
)

# Build RHS of controls with explicit factor() for categorical vars
cat_vars <- c("ur","Education_Level_HH_Head","Marital_Status_HH_Head","Year","Province")
num_vars <- setdiff(ctrls, cat_vars)
ctrl_rhs <- paste(
  c(sprintf("factor(%s)", cat_vars), num_vars),
  collapse = " + "
)

# Outcomes
outcomes <- c(
  "log_housing","log_total","log_food",
  "log_durables","log_education","log_transportation",
  "nroom","floor"
)


##  Clean numeric variables that may be stored as strings
consumption <- consumption %>%
  mutate(
    nroom = as.numeric(as.character(nroom)),
    floor = as.numeric(as.character(floor))
  )


##  Treatment indicators and instruments

# Post-period dummy (Persian calendar)
consumption$post <- as.integer(consumption$year %in% c( 1400,1401, 1402))

# Endogenous treatment: post × Afghan share
consumption$treat_endog <- consumption$post * consumption$afghan_pct

# Banned provinces indicator
consumption$Province <- as.character(consumption$Province)
consumption$banned   <- as.integer(consumption$Province %in% forbidden_provinces)
consumption$Province <- factor(consumption$Province)

# IV 1: post × afghan_share96
consumption$instr_iv <- consumption$post * consumption$afghan_share96

# IV 2: post × banned
consumption$instr_banned <- consumption$post * consumption$banned
# containers for models and clustered SEs
ols_models <- list()   # baseline DiD
ols_ses    <- list()

iv_models  <- list()   # IV–DiD (2SLS)
iv_ses     <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Outcome:", y, "\n")
  cat("======================================\n")

  # same sample definition for OLS and IV (so results are comparable)
  needed <- unique(c(
    y, "post","afghan_pct","treat_endog",
    "instr_iv","instr_banned",
    ctrls, "weight"
  ))
  dsub <- consumption[complete.cases(consumption[, needed]), needed, drop = FALSE]

  ## ----------  Baseline DiD (no IV) ----------
  # OLS: outcome on afghan_pct + treat_endog + controls + Year/Province FE
  fml_ols <- as.formula(paste0(
    y, " ~  + ", ctrl_rhs, " + treat_endog"
  ))

  m_ols <- lm(fml_ols, data = dsub, weights = weight)
  vc_ols <- vcovCL(m_ols, cluster = ~ Province)
  se_ols <- sqrt(diag(vc_ols))

  ols_models[[y]] <- m_ols
  ols_ses[[y]]    <- se_ols

  ## ----------  IV–DiD (two IVs) ----------
  # 2SLS: treat_endog instrumented by instr_iv & instr_banned
  fml_iv <- as.formula(paste0(
    y, " ~  + ", ctrl_rhs, " + treat_endog | ",
    " + ", ctrl_rhs, " + instr_iv + instr_banned"
  ))

  m_iv <- ivreg(fml_iv, data = dsub, weights = weight)
  vc_iv <- vcovCL(m_iv, cluster = ~ Province)
  se_iv <- sqrt(diag(vc_iv))

  iv_models[[y]] <- m_iv
  iv_ses[[y]]    <- se_iv

  # print IV results to console (clustered by Province)
  cat("\n--- IV–DiD (clustered SE, Province) ---\n")
  print(coeftest(m_iv, vcov = vc_iv))
  # =====  First-stage joint F for instr_iv & instr_banned =====
  # First-stage regression: treat_endog on instruments + controls
  fml_fs <- as.formula(paste0(
    "treat_endog ~ instr_iv + instr_banned + ", ctrl_rhs
  ))

  fs <- lm(fml_fs, data = dsub, weights = weight)

  cat("\n-- Province-clustered first-stage joint F (instr_iv & instr_banned) --\n")
  fs_F <- waldtest(
    fs,
    . ~ . - instr_iv - instr_banned,
    vcov = vcovCL(fs, cluster = ~ Province),
    test = "F"
  )
  print(fs_F)
}

# keep models in outcome order
ols_models_list <- unname(ols_models[outcomes])
ols_ses_list    <- unname(ols_ses[outcomes])

iv_models_list  <- unname(iv_models[outcomes])
iv_ses_list     <- unname(iv_ses[outcomes])

## ==================================================
##  Build LaTeX for Table 1 (Panel A / Panel B)
## ==================================================

# Panel A: Baseline DiD (no IV)
# only treatment coefficient shown; FE & controls omitted from table
panelA_latex <- capture.output(
  stargazer(
    ols_models_list,
    se = ols_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    title  = "Panel A: Baseline DiD (no IV)",
    dep.var.labels.include = FALSE,
    column.labels  = outcomes,
    column.separate = rep(1, length(outcomes)),
    omit = c("factor\\(", "afghan_pct"),   # hide FE + main share; keep DiD term
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# Panel B: IV–DiD (2SLS with two instruments)
panelB_latex <- capture.output(
  stargazer(
    iv_models_list,
    se = iv_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    title  = "Panel B: IV–DiD (2SLS, instruments: post×afghan\\_share96, post×banned)",
    dep.var.labels.include = FALSE,
    column.labels  = outcomes,
    column.separate = rep(1, length(outcomes)),
    omit = c("factor\\(", "afghan_pct"),   # same omission rule as Panel A
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share (IV)",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# write combined table to a single .tex file
table1_file <- "table_consumption_did_iv.tex"

cat(
  "% ==================================================\n",
  "% Table 1: Baseline DiD and IV–DiD\n",
  "% ==================================================\n",
  "\\begin{table}[ht]\\centering\n",
  "\\caption{Baseline DiD and IV–DiD estimates}\n",
  "\\label{tab:did_ivdid}\n\n",
  "% -------- Panel A --------\n",
  "\\textbf{Panel A: Baseline DiD (no IV)}\\\\[0.5em]\n",
  paste(panelA_latex, collapse = "\n"), "\n\n",
  "% -------- Panel B --------\n",
  "\\vspace{1em}\n",
  "\\textbf{Panel B: IV--DiD (2SLS)}\\\\[0.5em]\n",
  paste(panelB_latex, collapse = "\n"), "\n",
  "\\end{table}\n",
  file = table1_file
)



```



### Main Analysis With Post-2022. 
```{r}
## ==================================================
##  Baseline DiD (no IV) and IV–DiD (two IVs)
##    + export to LaTeX as Table 1 (Panel A/B)
## ==================================================

consumption <- consumption %>%
  filter(year %in% 1397:1402) %>%
  filter(complete.cases(across(all_of(c(vars_summ, "weight")))))



##  Construct afghan_share96 (province share of total Afghans in 1996)
consumption <- consumption %>%
  group_by(Province) %>%
  mutate(
    # Provincial Afghan count in 1996 (same within province)
    Afghans_prov = first(Afghans)
  ) %>%
  ungroup() %>%
  mutate(
    # Total Afghan population in 1996 across provinces
    total_Afghans_1996 = sum(Afghans_prov, na.rm = TRUE),
    # Province share of national Afghan total
    afghan_share96      = Afghans_prov / total_Afghans_1996
  ) %>%
  select(-Afghans_prov, -total_Afghans_1996)


##  Define banned provinces (for second IV)
forbidden_provinces <- c(
  "East Azerbaijan","West Azerbaijan","Ardabil","Zanjan",
  "Kurdistan","Kermanshah","Ilam","Chaharmahal and Bakhtiari",
  "Kohgiluyeh and Boyer-Ahmad","North Khorasan","Gilan",
  "Mazandaran","Sistan and Baluchestan","Khuzestan",
  "Hamadan","Lorestan"
)

# List of controls (Year and Province included for FE)
ctrls <- c(
  "ur","Num_HH_Members","Num_Male",
  "Num_Under14","Num_Over65",
  "Education_Level_HH_Head","Marital_Status_HH_Head",
  "ntl","pop_density","Year","Province"
)

# Build RHS of controls with explicit factor() for categorical vars
cat_vars <- c("ur","Education_Level_HH_Head","Marital_Status_HH_Head","Year","Province")
num_vars <- setdiff(ctrls, cat_vars)
ctrl_rhs <- paste(
  c(sprintf("factor(%s)", cat_vars), num_vars),
  collapse = " + "
)

# Outcomes
outcomes <- c(
  "log_housing","log_total","log_food",
  "log_durables","log_education","log_transportation",
  "nroom","floor"
)


##  Clean numeric variables that may be stored as strings
consumption <- consumption %>%
  mutate(
    nroom = as.numeric(as.character(nroom)),
    floor = as.numeric(as.character(floor))
  )


##  Treatment indicators and instruments

# Post-period dummy (Persian calendar)
consumption$post <- as.integer(consumption$year %in% c(1401, 1402))

# Endogenous treatment: post × Afghan share
consumption$treat_endog <- consumption$post * consumption$afghan_pct

# Banned provinces indicator
consumption$Province <- as.character(consumption$Province)
consumption$banned   <- as.integer(consumption$Province %in% forbidden_provinces)
consumption$Province <- factor(consumption$Province)

# IV 1: post × afghan_share96
consumption$instr_iv <- consumption$post * consumption$afghan_share96

# IV 2: post × banned
consumption$instr_banned <- consumption$post * consumption$banned
# containers for models and clustered SEs
ols_models <- list()   # baseline DiD
ols_ses    <- list()

iv_models  <- list()   # IV–DiD (2SLS)
iv_ses     <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Outcome:", y, "\n")
  cat("======================================\n")

  # same sample definition for OLS and IV (so results are comparable)
  needed <- unique(c(
    y, "post","afghan_pct","treat_endog",
    "instr_iv","instr_banned",
    ctrls, "weight"
  ))
  dsub <- consumption[complete.cases(consumption[, needed]), needed, drop = FALSE]

  ## ----------  Baseline DiD (no IV) ----------
  # OLS: outcome on afghan_pct + treat_endog + controls + Year/Province FE
  fml_ols <- as.formula(paste0(
    y, " ~  + ", ctrl_rhs, " + treat_endog"
  ))

  m_ols <- lm(fml_ols, data = dsub, weights = weight)
  vc_ols <- vcovCL(m_ols, cluster = ~ Province)
  se_ols <- sqrt(diag(vc_ols))

  ols_models[[y]] <- m_ols
  ols_ses[[y]]    <- se_ols

  ## ----------  IV–DiD (two IVs) ----------
  # 2SLS: treat_endog instrumented by instr_iv & instr_banned
  fml_iv <- as.formula(paste0(
    y, " ~  + ", ctrl_rhs, " + treat_endog | ",
    " + ", ctrl_rhs, " + instr_iv + instr_banned"
  ))

  m_iv <- ivreg(fml_iv, data = dsub, weights = weight)
  vc_iv <- vcovCL(m_iv, cluster = ~ Province)
  se_iv <- sqrt(diag(vc_iv))

  iv_models[[y]] <- m_iv
  iv_ses[[y]]    <- se_iv

  # print IV results to console (clustered by Province)
  cat("\n--- IV–DiD (clustered SE, Province) ---\n")
  print(coeftest(m_iv, vcov = vc_iv))
  # =====  First-stage joint F for instr_iv & instr_banned =====
  # First-stage regression: treat_endog on instruments + controls
  fml_fs <- as.formula(paste0(
    "treat_endog ~ instr_iv + instr_banned + ", ctrl_rhs
  ))

  fs <- lm(fml_fs, data = dsub, weights = weight)

  cat("\n-- Province-clustered first-stage joint F (instr_iv & instr_banned) --\n")
  fs_F <- waldtest(
    fs,
    . ~ . - instr_iv - instr_banned,
    vcov = vcovCL(fs, cluster = ~ Province),
    test = "F"
  )
  print(fs_F)
}

# keep models in outcome order
ols_models_list <- unname(ols_models[outcomes])
ols_ses_list    <- unname(ols_ses[outcomes])

iv_models_list  <- unname(iv_models[outcomes])
iv_ses_list     <- unname(iv_ses[outcomes])

## ==================================================
##  Build LaTeX for Table 1 (Panel A / Panel B)
## ==================================================

# Panel A: Baseline DiD (no IV)
# only treatment coefficient shown; FE & controls omitted from table
panelA_latex <- capture.output(
  stargazer(
    ols_models_list,
    se = ols_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    title  = "Panel A: Baseline DiD (no IV)",
    dep.var.labels.include = FALSE,
    column.labels  = outcomes,
    column.separate = rep(1, length(outcomes)),
    omit = c("factor\\(", "afghan_pct"),   # hide FE + main share; keep DiD term
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# Panel B: IV–DiD (2SLS with two instruments)
panelB_latex <- capture.output(
  stargazer(
    iv_models_list,
    se = iv_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    title  = "Panel B: IV–DiD (2SLS, instruments: post×afghan\\_share96, post×banned)",
    dep.var.labels.include = FALSE,
    column.labels  = outcomes,
    column.separate = rep(1, length(outcomes)),
    omit = c("factor\\(", "afghan_pct"),   # same omission rule as Panel A
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share (IV)",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# write combined table to a single .tex file
table1_file <- "table_consumption_did_iv_Post2022.tex"

cat(
  "% ==================================================\n",
  "% Table 1: Baseline DiD and IV–DiD\n",
  "% ==================================================\n",
  "\\begin{table}[ht]\\centering\n",
  "\\caption{Baseline DiD and IV–DiD estimates}\n",
  "\\label{tab:did_ivdid}\n\n",
  "% -------- Panel A --------\n",
  "\\textbf{Panel A: Baseline DiD (no IV)}\\\\[0.5em]\n",
  paste(panelA_latex, collapse = "\n"), "\n\n",
  "% -------- Panel B --------\n",
  "\\vspace{1em}\n",
  "\\textbf{Panel B: IV--DiD (2SLS)}\\\\[0.5em]\n",
  paste(panelB_latex, collapse = "\n"), "\n",
  "\\end{table}\n",
  file = table1_file
)



```


# Supply Side Analysis


### Table 2: Supply side: summary statistics

```{r}


construction <- read_dta("construction_final.dta") %>%
  filter(year != 1403)

vars <- c(
  "total_permits", "residential_permits",
  "total_land", "residential_land",
  "total_floor", "residential_floor",
  "total_units", "residential_units",
  "afghan_pop", "ntl", "pop_density"
)

## Keep only variables that are present in the data
vars <- vars[vars %in% names(construction)]

## 3. Compute summary statistics
summ_list <- lapply(vars, function(v) {
  x <- construction[[v]]
  x <- x[!is.na(x)]
  c(
    N      = length(x),
    Mean   = mean(x),
    SD     = sd(x),
    Min    = min(x),
    P25    = as.numeric(quantile(x, 0.25)),
    Median = as.numeric(quantile(x, 0.50)),
    P75    = as.numeric(quantile(x, 0.75)),
    Max    = max(x)
  )
})

summary_table <- do.call(rbind, summ_list)
summary_table <- data.frame(
  Variable = vars,
  summary_table,
  row.names = NULL,
  check.names = FALSE
)

## 4. Optional: round numeric columns for display/LaTeX
num_cols <- setdiff(names(summary_table), "Variable")
summary_table[num_cols] <- lapply(summary_table[num_cols], function(z) round(z, 3))
summary_table$N <- as.integer(summary_table$N)

## 5. Print table in R
print(summary_table)

## 6. Export to LaTeX
latex_table <- xtable(
  summary_table,
  caption = "Summary statistics: construction dataset",
  label   = "tab:summary_construction"
)

print(
  latex_table,
  include.rownames = FALSE,
  file = "summary_construction.tex"
)

```




### Table 4:  IV-DiD 



```{r}


construction <- read_dta("construction_final.dta")

construction$Province <- factor(construction$Province)
construction$year     <- as.factor(construction$year)
construction$quarter  <- as.factor(construction$quart)

# ===== 2) Drop 1403 (2024) ===== # this happens because we do not have inflow of of Afghans in 2024
construction <- subset(construction, year != 1403)

# ===== 3) Import 1375 census & merge instrument component =====
sar <- read_xlsx("Sarshomari_1375.xlsx")  # has Province, Afghans, ...
sar$Share_allAfghans <- sar$Afghans / sum(sar$Afghans, na.rm = TRUE)
sar_keep <- sar[, c("Province", "Share_allAfghans")]

construction <- merge(construction, sar_keep, by = "Province", all.x = TRUE)

# ===== 4) Define post, endogenous, and instruments =====
construction$post        <- as.integer(construction$year %in% c(1401, 1402))
construction$treat_endog <- construction$post * construction$afghan_pct
construction$instr1      <- construction$post * construction$Share_allAfghans   # historical (shift-share)
construction$instr2      <- construction$post * construction$banned             # policy-based

# ===== 5) Controls, FE, outcomes =====
ctrl_rhs <- "ntl + pop_density + factor(Province) + factor(year) + factor(quart)"
outcomes <- c(
  "total_permits","residential_permits",
  "total_land","residential_land",
  "total_floor","residential_floor",
  "total_units","residential_units"
)

# ===== 6) Storage for LaTeX (OLS and IV) =====
ols_models_list <- list()
iv_models_list  <- list()
ols_ses_list    <- list()
iv_ses_list     <- list()

# ===== 7) Loop over outcomes =====
for (y in outcomes) {
  cat("\n======================================\nOutcome:", y, "\n======================================\n")

  # ---------- 7A) Baseline DiD (OLS, no IV) ----------
  fml_ols <- as.formula(paste0(
    y, " ~ treat_endog + ", ctrl_rhs
  ))

  ols <- lm(fml_ols, data = construction)

  # rows actually used by the model (after na.omit)
  mf_ols  <- model.frame(ols)
  idx_ols <- match(rownames(mf_ols), rownames(construction))

  # Province  clustering
  V_ols_prov <- cluster.vcov(
    ols,
    construction$Province[idx_ols]
  )

  ols_models_list[[y]] <- ols
  ols_ses_list[[y]]    <- sqrt(diag(V_ols_prov))

  # ---------- 7B) IV–DiD (2SLS with two instruments) ----------
  fml_iv <- as.formula(paste0(
    y, " ~  + ", ctrl_rhs, " + treat_endog | ",
    " + ", ctrl_rhs, " + instr1 + instr2"
  ))

  m <- ivreg(fml_iv, data = construction)

  mf_iv  <- model.frame(m)
  idx_iv <- match(rownames(mf_iv), rownames(construction))

  V_prov <- cluster.vcov(
    m,
    construction$Province[idx_iv]
  )

  # print ONLY IV–DiD results
  print(coeftest(m, vcov = V_prov))

  iv_models_list[[y]] <- m
  iv_ses_list[[y]]    <- sqrt(diag(V_prov))

  # ---------- 7C) First-stage joint F for instr1 & instr2 ----------
  fml_fs <- as.formula(paste0(
    "treat_endog ~ instr1 + instr2 + ", ctrl_rhs
  ))

  fs <- lm(fml_fs, data = construction)

  mf_fs  <- model.frame(fs)
  idx_fs <- match(rownames(mf_fs), rownames(construction))

  V_prov_fs <- cluster.vcov(
    fs,
    construction$Province[idx_fs]
  )

  cat("\n-- Province-clustered first-stage joint F (instr1 & instr2) --\n")
  print(waldtest(fs, . ~ . - instr1 - instr2, vcov = V_prov_fs))
}

# Align lists just in case
iv_models_list  <- Filter(Negate(is.null), iv_models_list)
ols_models_list <- ols_models_list[names(iv_models_list)]
ols_ses_list    <- ols_ses_list[names(iv_models_list)]
iv_ses_list     <- iv_ses_list[names(iv_models_list)]

# ==================================================
# 8. Build LaTeX: Panel A (OLS DiD) + Panel B (IV–DiD)
# ==================================================

# Panel A: Baseline DiD (no IV)
panelA_latex <- capture.output(
  stargazer(
    ols_models_list,
    se = ols_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    dep.var.labels.include = FALSE,
    column.labels   = names(ols_models_list),
    column.separate = rep(1, length(ols_models_list)),
    omit = c("factor\\(", "afghan_pct", "ntl", "pop_density"),
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# Panel B: IV–DiD (2SLS with two instruments)
panelB_latex <- capture.output(
  stargazer(
    iv_models_list,
    se = iv_ses_list,
    type = "latex",
    header = FALSE,
    table  = FALSE,
    dep.var.labels.include = FALSE,
    column.labels   = names(iv_models_list),
    column.separate = rep(1, length(iv_models_list)),
    omit = c("factor\\(", "afghan_pct", "ntl", "pop_density",
             "instr1", "instr2"),
    keep = "treat_endog",
    covariate.labels = "Post × Afghan share (2SLS)",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

full_latex <- c(
  "\\begin{table}[!htbp]\\centering",
  "\\caption{Difference-in-differences estimates: construction outcomes}",
  "\\label{tab:construction_did_iv}",
  "\\begin{center}",
  "\\textbf{Panel A: Baseline DiD (no IV)}\\\\",
  panelA_latex,
  "\\\\[1em]",
  "\\textbf{Panel B: IV--DiD (2SLS with two instruments)}\\\\",
  panelB_latex,
  "\\end{center}",
  "\\end{table}"
)

writeLines(full_latex, "table_construction_did_iv.tex")



```









# Appendix

### Robustness Checks


### Table 5(Appendix): DiD of Consumption outcomes
```{r}

 ## ==================================================
## Continuous DiD: Afghan pre-settlement exposure × post
## ==================================================
# List of controls (Year and Province included for FE)
ctrls <- c(
  "ur","Num_HH_Members","Num_Male",
  "Num_Under14","Num_Over65",
  "Education_Level_HH_Head","Marital_Status_HH_Head",
  "ntl","pop_density","Year","Province"
)

# Build RHS of controls with explicit factor() for categorical vars
cat_vars <- c("ur","Education_Level_HH_Head","Marital_Status_HH_Head","Year","Province")
num_vars <- setdiff(ctrls, cat_vars)
ctrl_rhs <- paste(
  c(sprintf("factor(%s)", cat_vars), num_vars),
  collapse = " + "
)

# Outcomes
outcomes <- c(
  "log_housing","log_total","log_food",
  "log_durables","log_education","log_transportation",
  "nroom","floor"
)

# Post dummy: 1400–1402 are post
consumption$post_did <- as.integer(consumption$year %in% c(1400, 1401, 1402))

# Continuous DiD treatment: pre-settlement share × post
# (afghan_share75 is the pre-settlement exposure)
# Rename the pre-settlement exposure variable (old: afghan_share75)
consumption <- consumption %>%
  mutate (afghan_settlement_pct96 = afghan_share75 * 100)

# afghan_settlement_share96:
#   Share of Afghans in each province relative to the *province's total population* in 1996.
#   This is the "pre-settlement exposure" variable used in the DiD identification strategy
#   (similar to Rozo 2021). Higher values indicate provinces that historically hosted a
#   larger Afghan presence relative to their own native population.

# Note the difference from afghan_share96 (used in the IV-DiD):
#   - afghan_settlement_share96 = Afghans_prov_1996 / total_population_prov_1996
#       → exposure of the *local population* to Afghans historically.
#
#   - afghan_share96 = Afghans_prov_1996 / total_Afghans_1996
#       → province's share of the *national Afghan population* in 1996.

consumption$treat_did <- consumption$post_did * consumption$afghan_settlement_pct96


# Containers for models and clustered SEs
did_models <- list()
did_ses    <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Outcome:", y, "\n")
  cat("======================================\n")
  
  # DiD specification:
  #   - treat_did is the key DiD term: afghan_share75 × post_did
  #   - ctrl_rhs already includes Year and Province FE and other controls
  fml <- as.formula(paste0(
    y, " ~ treat_did + ", ctrl_rhs
  ))
  
  needed <- unique(c(
    y,
    "treat_did",
    ctrls,
    "weight",
    "afghan_settlement_pct96"
  ))
  
  dsub <- consumption[complete.cases(consumption[, needed]), needed, drop = FALSE]
  
  # Weighted OLS with clustered SE at Province level
  m  <- lm(fml, data = dsub, weights = weight)
  vc <- vcovCL(m, cluster = ~ Province)
  
  did_models[[y]] <- m
  did_ses[[y]]    <- sqrt(diag(vc))
  
  # Print regression with clustered SE
  print(coeftest(m, vcov = vc))
}

# Keep models in the same order as "outcomes"
did_models_list <- unname(did_models[outcomes])
did_ses_list    <- unname(did_ses[outcomes])


## ==================================================
## LaTeX table: Continuous DiD (Afghan pre-settlement × post)
## ==================================================

did_table_tex <- capture.output(
  stargazer(
    did_models_list,
    se = did_ses_list,
    type = "latex",
    summary = FALSE,
    header  = FALSE,
    title   = "Continuous DiD: Afghan pre-settlement exposure and consumption outcomes",
    label   = "tab:did_afghan_share75",
    dep.var.labels.include = FALSE,
    column.labels   = outcomes,
    column.separate = rep(1, length(outcomes)),
    keep = "treat_did",
    covariate.labels = "Post × Afghan pre-settlement exposure",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# Write LaTeX file
cat(did_table_tex, sep = "\n",
    file = "table_did_afghan_pct96.tex")



```



### Figure 6: Event Study of consumption outcomes



```{r}
## ==================================================
## Dynamic DiD (event study):
## Afghan pre-settlement exposure × Year (2020 ref.)
## ==================================================


# Years in the panel (Gregorian)
years_all <- sort(unique(consumption$Year))
ref_year  <- 2020L

# Years that get their own interaction terms (all except 2020)
es_years <- years_all[years_all != ref_year]

# For each year t ≠ 2020 define:
#   treat_es_t = afghan_settlement_share96 * 1{Year == t}
# There is deliberately NO treat_es_2020 → β_2020 is normalized to zero.
for (yr in es_years) {
  varname <- paste0("treat_es_", yr)
  consumption[[varname]] <- ifelse(
    consumption$Year == yr,
    consumption$afghan_settlement_pct96,
    0
  )
}

treat_es_vars <- paste0("treat_es_", es_years)

# Containers for models and clustered vcov
es_models <- list()
es_ses    <- list()
es_vcovs  <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Dynamic DiD – Outcome:", y, "\n")
  cat("======================================\n")
  
  # Event-study specification:
  #   y_pyt = sum_{t≠2020} β_t * (afghan_settlement_share96_p × 1{Year_t})
  #           + Province FE + Year FE + controls + ε
  fml_es <- as.formula(paste0(
    y, " ~ ", ctrl_rhs, " + ", paste(treat_es_vars, collapse = " + ")
  ))
  
  needed <- unique(c(
    y,
    "afghan_settlement_pct96",
    "Year",
    ctrls,
    "weight",
    treat_es_vars
  ))
  
  dsub <- consumption[complete.cases(consumption[, needed]), needed, drop = FALSE]
  
  m_es  <- lm(fml_es, data = dsub, weights = weight)
  vc_es <- vcovCL(m_es, cluster = ~ Province)
  
  es_models[[y]] <- m_es
  es_ses[[y]]    <- sqrt(diag(vc_es))
  es_vcovs[[y]]  <- vc_es
  
  print(coeftest(m_es, vcov = vc_es))
}

es_models_list <- unname(es_models[outcomes])
es_ses_list    <- unname(es_ses[outcomes])
es_vcovs_list  <- unname(es_vcovs[outcomes])


## ==================================================
## LaTeX table: Dynamic DiD (event study)
## ==================================================

es_table_tex <- capture.output(
  stargazer(
    es_models_list,
    se     = es_ses_list,
    type   = "latex",
    summary = FALSE,
    header  = FALSE,
    title   = "Dynamic DiD (event study) with Afghan pre-settlement exposure",
    label   = "tab:event_study_afghan_settlement",
    dep.var.labels.include = FALSE,
    column.labels   = outcomes,
    column.separate = rep(1, length(outcomes)),
    keep   = "treat_es_",
    notes  = "Cluster-robust standard errors at the province level in parentheses. Year 2020 is the reference period (effect normalized to zero)."
  )
)

cat(es_table_tex, sep = "\n",
    file = "table_event_study_afghan_settlement.tex")

event_study_table_tex <- es_table_tex   # keep in environment


## ==================================================
## Event-study plot (faceted, 2020 = 0)
## ==================================================

# Extract dynamic coefficients for one model
extract_es <- function(mod, vcov_mat, ref_year) {
  cf   <- coef(mod)
  vcv  <- diag(vcov_mat)
  nm   <- names(cf)
  
  idx  <- grep("^treat_es_", nm)
  if (length(idx) == 0) return(NULL)
  
  beta <- cf[idx]
  se   <- sqrt(vcv[idx])
  
  years <- as.integer(sub("treat_es_", "", nm[idx]))
  
  df_es <- data.frame(
    year  = years,
    beta  = beta,
    se    = se
  )
  
  df_es$lower <- df_es$beta - 1.96 * df_es$se
  df_es$upper <- df_es$beta + 1.96 * df_es$se
  
  # Add the reference year (2020) with zero effect and no CI
  df_es <- rbind(
    df_es,
    data.frame(
      year  = ref_year,
      beta  = 0,
      se    = NA_real_,
      lower = NA_real_,
      upper = NA_real_
    )
  )
  
  df_es[order(df_es$year), ]
}

# Build a single data frame for all outcomes
es_plot_df <- do.call(
  rbind,
  lapply(seq_along(outcomes), function(i) {
    y   <- outcomes[i]
    mod <- es_models_list[[i]]
    vc  <- es_vcovs_list[[i]]
    
    df <- extract_es(mod, vc, ref_year)
    if (is.null(df)) return(NULL)
    df$outcome <- y
    df
  })
)

p_es <- ggplot(es_plot_df, aes(x = year, y = beta)) +
  # grey vertical band for the reference year
  annotate(
    "rect",
    xmin = ref_year - 0.5, xmax = ref_year + 0.5,
    ymin = -Inf, ymax = Inf,
    alpha = 0.3, fill = "grey70"
  ) +
  # horizontal zero line
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  # connected line and points
  geom_line(colour = "black") +
  geom_point(colour = "black", size = 2) +
  # confidence intervals
  geom_errorbar(aes(ymin = lower, ymax = upper),
                width = 0.15, colour = "black") +
  # one panel per outcome
  facet_wrap(~ outcome, scales = "free_y") +
  # clean layout
  theme_bw() +
  theme(
    strip.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black"),
    axis.title.x = element_text(size = 11),
    axis.title.y = element_text(size = 11),
    plot.title = element_text(size = 13, face = "bold")
  ) +
  labs(
   # title = "Dynamic DiD (Event Study): Year × Afghan pre-settlement exposure",
    x = "Year",
    y = "Year × Afghan pre-settlement exposure"
  )

print(p_es)

ggsave(
  filename = "event_study_afghan_settlement.png",
  plot     = p_es,
  width    = 9,
  height   = 7,
  bg       = "white"
)


```





###  DiD Construction
```{r}

 ## ==================================================
## Continuous DiD: Afghan pre-settlement exposure × post
## ==================================================


ctrl_rhs <- "ntl + pop_density + factor(Province) + factor(year) + factor(quart)"
outcomes <- c(
  "total_permits","residential_permits",
  "total_land","residential_land",
  "total_floor","residential_floor",
  "total_units","residential_units"
)

construction <- read_dta("construction_final.dta")

construction$Province <- factor(construction$Province)
construction$year     <- as.factor(construction$year)
construction$quarter  <- as.factor(construction$quart)
construction <- subset(construction, year != 1403)


# Post dummy: 1400–1402 are post
construction$post_did <- as.integer(construction$year %in% c(1400,1401, 1402))

# Continuous DiD treatment: pre-settlement share × post
# (afghan_share75 is the pre-settlement exposure)
# Rename the pre-settlement exposure variable (old: afghan_share75)
construction <- construction %>%
  mutate (afghan_settlement_pct96 = Share_75 * 100)

# afghan_settlement_share96:
#   Share of Afghans in each province relative to the *province's total population* in 1996.
#   This is the "pre-settlement exposure" variable used in the DiD identification strategy
#   (similar to Rozo 2021). Higher values indicate provinces that historically hosted a
#   larger Afghan presence relative to their own native population.

# Note the difference from afghan_share96 (used in the IV-DiD):
#   - afghan_settlement_share96 = Afghans_prov_1996 / total_population_prov_1996
#       → exposure of the *local population* to Afghans historically.
#
#   - afghan_share96 = Afghans_prov_1996 / total_Afghans_1996
#       → province's share of the *national Afghan population* in 1996.

construction$treat_did <- construction$post_did * construction$afghan_settlement_pct96


# Containers for models and clustered SEs
did_models <- list()
did_ses    <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Outcome:", y, "\n")
  cat("======================================\n")
  
  # DiD specification:
  #   - treat_did is the key DiD term: afghan_share75 × post_did
  #   - ctrl_rhs already includes Year and Province FE and other controls
  fml <- as.formula(paste0(
    y, " ~ treat_did + ", ctrl_rhs
  ))
  
  
  
  # Weighted OLS with clustered SE at Province level
  m  <- lm(fml, data = construction)
  vc <- vcovCL(m, cluster = ~ Province)
  
  did_models[[y]] <- m
  did_ses[[y]]    <- sqrt(diag(vc))
  
  # Print regression with clustered SE
  print(coeftest(m, vcov = vc))
}

# Keep models in the same order as "outcomes"
did_models_list <- unname(did_models[outcomes])
did_ses_list    <- unname(did_ses[outcomes])


## ==================================================
## LaTeX table: Continuous DiD (Afghan pre-settlement × post)
## ==================================================

did_table_tex <- capture.output(
  stargazer(
    did_models_list,
    se = did_ses_list,
    type = "latex",
    summary = FALSE,
    header  = FALSE,
    title   = "Continuous DiD: Afghan pre-settlement exposure and construction outcomes",
    label   = "tab:did_afghan_share75",
    dep.var.labels.include = FALSE,
    column.labels   = outcomes,
    column.separate = rep(1, length(outcomes)),
    keep = "treat_did",
    covariate.labels = "Post × Afghan pre-settlement exposure",
    notes = "Cluster-robust standard errors at the province level in parentheses."
  )
)

# Write LaTeX file
cat(did_table_tex, sep = "\n",
    file = "table_did_afghan_pct96_construction_post2021.tex")



```


### Event Study Construction

```{r}


ctrl_rhs <- "ntl + pop_density + factor(Province) + factor(year) + factor(quart)"
outcomes <- c(
  "total_permits","residential_permits",
  "total_land","residential_land",
  "total_floor","residential_floor",
  "total_units","residential_units"
)

construction <- read_dta("construction_final.dta")

construction$Province <- factor(construction$Province)
construction$year     <- as.factor(construction$year)
construction$quarter  <- as.factor(construction$quart)
construction <- subset(construction, year != 1403)

construction <- construction %>%
  mutate (afghan_settlement_pct96 = Share_75 * 100)

construction <- construction %>%
  mutate(
    Year = dplyr::recode(
      year,
      `1397` = 2018,
      `1398` = 2019,
      `1399` = 2020,
      `1400` = 2021,
      `1401` = 2022,
      `1402` = 2023
      )
  )


ctrl_rhs <- "ntl + pop_density + factor(Province) + factor(year) + factor(quart)"

# Years in the panel (Gregorian)
years_all <- sort(unique(construction$Year))
ref_year  <- 2020L

# Years that get their own interaction terms (all except 2020)
es_years <- years_all[years_all != ref_year]

# For each year t ≠ 2020 define:
#   treat_es_t = afghan_settlement_share96 * 1{Year == t}
# There is deliberately NO treat_es_2020 → β_2020 is normalized to zero.
for (yr in es_years) {
  varname <- paste0("treat_es_", yr)
  construction[[varname]] <- ifelse(
    construction$Year == yr,
    construction$afghan_settlement_pct96,
    0
  )
}

treat_es_vars <- paste0("treat_es_", es_years)

# Containers for models and clustered vcov
es_models <- list()
es_ses    <- list()
es_vcovs  <- list()

for (y in outcomes) {
  cat("\n======================================\n")
  cat("Dynamic DiD – Outcome:", y, "\n")
  cat("======================================\n")
  
  # Event-study specification:
  #   y_pyt = sum_{t≠2020} β_t * (afghan_settlement_share96_p × 1{Year_t})
  #           + Province FE + Year FE + controls + ε
  fml_es <- as.formula(paste0(
    y, " ~ ", ctrl_rhs, " + ", paste(treat_es_vars, collapse = " + ")
  ))
  
 

  m_es  <- lm(fml_es, data = construction)
  vc_es <- vcovCL(m_es, cluster = ~ Province)
  
  es_models[[y]] <- m_es
  es_ses[[y]]    <- sqrt(diag(vc_es))
  es_vcovs[[y]]  <- vc_es
  
  print(coeftest(m_es, vcov = vc_es))
}

es_models_list <- unname(es_models[outcomes])
es_ses_list    <- unname(es_ses[outcomes])
es_vcovs_list  <- unname(es_vcovs[outcomes])


## ==================================================
## LaTeX table: Dynamic DiD (event study)
## ==================================================

es_table_tex <- capture.output(
  stargazer(
    es_models_list,
    se     = es_ses_list,
    type   = "latex",
    summary = FALSE,
    header  = FALSE,
    title   = "Dynamic DiD (event study) with Afghan pre-settlement exposure",
    label   = "tab:event_study_afghan_settlement",
    dep.var.labels.include = FALSE,
    column.labels   = outcomes,
    column.separate = rep(1, length(outcomes)),
    keep   = "treat_es_",
    notes  = "Cluster-robust standard errors at the province level in parentheses. Year 2020 is the reference period (effect normalized to zero)."
  )
)

cat(es_table_tex, sep = "\n",
    file = "table_event_study_afghan_settlement_construction.tex")

event_study_table_tex <- es_table_tex   # keep in environment


## ==================================================
## Event-study plot 
## ==================================================

# Extract dynamic coefficients for one model
extract_es <- function(mod, vcov_mat, ref_year) {
  cf   <- coef(mod)
  vcv  <- diag(vcov_mat)
  nm   <- names(cf)
  
  idx  <- grep("^treat_es_", nm)
  if (length(idx) == 0) return(NULL)
  
  beta <- cf[idx]
  se   <- sqrt(vcv[idx])
  
  years <- as.integer(sub("treat_es_", "", nm[idx]))
  
  df_es <- data.frame(
    year  = years,
    beta  = beta,
    se    = se
  )
  
  df_es$lower <- df_es$beta - 1.96 * df_es$se
  df_es$upper <- df_es$beta + 1.96 * df_es$se
  
  # Add the reference year (2020) with zero effect and no CI
  df_es <- rbind(
    df_es,
    data.frame(
      year  = ref_year,
      beta  = 0,
      se    = NA_real_,
      lower = NA_real_,
      upper = NA_real_
    )
  )
  
  df_es[order(df_es$year), ]
}

# Build a single data frame for all outcomes
es_plot_df <- do.call(
  rbind,
  lapply(seq_along(outcomes), function(i) {
    y   <- outcomes[i]
    mod <- es_models_list[[i]]
    vc  <- es_vcovs_list[[i]]
    
    df <- extract_es(mod, vc, ref_year)
    if (is.null(df)) return(NULL)
    df$outcome <- y
    df
  })
)

p_es <- ggplot(es_plot_df, aes(x = year, y = beta)) +
  # grey vertical band for the reference year
  annotate(
    "rect",
    xmin = ref_year - 0.5, xmax = ref_year + 0.5,
    ymin = -Inf, ymax = Inf,
    alpha = 0.3, fill = "grey70"
  ) +
  # horizontal zero line
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  # connected line and points
  geom_line(colour = "black") +
  geom_point(colour = "black", size = 2) +
  # confidence intervals
  geom_errorbar(aes(ymin = lower, ymax = upper),
                width = 0.15, colour = "black") +
  # one panel per outcome
  facet_wrap(~ outcome, scales = "free_y") +
  # clean layout
  theme_bw() +
  theme(
    strip.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black"),
    axis.title.x = element_text(size = 11),
    axis.title.y = element_text(size = 11),
    plot.title = element_text(size = 13, face = "bold")
  ) +
  labs(
   # title = "Dynamic DiD (Event Study): Year × Afghan pre-settlement exposure",
    x = "Year",
    y = "Year × Afghan pre-settlement exposure"
  )

print(p_es)

ggsave(
  filename = "event_study_afghan_settlement_constructionpost-2021.png",
  plot     = p_es,
  width    = 9,
  height   = 7,
  bg       = "white"
)


```


### Figure 2: Heat Maps- Afghan Share(2023 vs 1996)


```{r}

## 1) Read Iran shapefile + data
iran <- sf::st_read(
  "Mapping/iranmap/irn_admbnda_adm1_unhcr_20190514.shp"
) %>%
  rename(Province = ADM1_EN)

sarshomari_1375 <- read_xlsx("Sarshomari_1375.xlsx")
LFS             <- read_dta("LFS.dta")

## 2) 1996 – make it PERCENT (Afghans / Total * 100)
sarshomari_1375 <- sarshomari_1375 %>%
  mutate(
    Afghans = as.numeric(Afghans),
    Total   = as.numeric(Total),
    Afghan_pct_1375 = 100 * Afghans / Total
  ) %>%
  select(Province, Afghan_pct_1375)

## 3) 1402 – LFS subset and province-level percent
LFS402 <- LFS %>% filter(year == 402)

lfs_1402 <- LFS402 %>%
  rename(Province = province_name,
         afghan_pct_1402=afghan_pct)

## 4) Merge both years to map
iran <- iran %>%
  left_join(sarshomari_1375, by = "Province") %>%
  left_join(lfs_1402,        by = "Province")

iran_border <- sf::st_union(iran)

## 5) Long format for faceting
iran_long <- iran %>%
  select(Province, Afghan_pct_1375, afghan_pct_1402, geometry) %>%
  pivot_longer(
    cols      = c(Afghan_pct_1375, afghan_pct_1402),
    names_to  = "year",
    values_to = "afghan_share"
  ) %>%
  mutate(
    year = dplyr::recode(
      year,
      "Afghan_pct_1375" = "Afghan Population Share,1996",
      "afghan_pct_1402" = "Afghan Population Share,2023"
    ),
    year = factor(
      year,
      levels = c("Afghan Population Share,1996",
                 "Afghan Population Share,2023")
    )
  )

## 6) Palette + common range
blue_pal  <- colorRampPalette(c("white", "#08519c"))(100)
val_range <- range(iran_long$afghan_share, na.rm = TRUE)

## 6.5) Correlation + significance stars (ONE value)
corr_data <- iran %>%
  st_drop_geometry() %>%
  select(Afghan_pct_1375, afghan_pct_1402) %>%
  na.omit()

corr_test <- cor.test(
  corr_data$Afghan_pct_1375,
  corr_data$afghan_pct_1402
)

corr_val <- unname(corr_test$estimate)
p_val    <- corr_test$p.value

stars <- {
  if (p_val < 0.001) {
    "***"
  } else if (p_val < 0.01) {
    "**"
  } else if (p_val < 0.05) {
    "*"
  } else {
    ""
  }
}

corr_label <- sprintf("Correlation (1996 vs 2023) = %.3f%s",
                      corr_val, stars)

## 7) Final two-panel map with ONE centered correlation caption
ggplot() +
  geom_sf(
    data  = iran_long,
    aes(fill = afghan_share),
    color = "grey70",
    size  = 0.3
  ) +
  geom_sf(
    data        = iran_border,
    fill        = NA,
    color       = "black",
    size        = 0.6,
    inherit.aes = FALSE
  ) +
  facet_wrap(~ year, ncol = 2) +
  scale_fill_gradientn(
    colours  = blue_pal,
    na.value = "#f0f0f0",
    limits   = val_range,
    name     = "Share (%)"
  ) +
  labs(caption = corr_label) +
  theme_void() +
  theme(
    legend.position   = "bottom",
    strip.text        = element_text(size = 11, face = "bold"),
    plot.margin       = margin(5, 5, 5, 5),
    plot.caption      = element_text(hjust = 0.5, vjust = 1,
                                     size = 10, face = "bold")
  )
ggsave(
  filename = "Afghan_Population_Share_1996_2023.png",
  plot     = last_plot(),   # saves the most recent ggplot
  width    = 10,            # inches
  height   = 6,
  dpi      = 300,
  bg       = "white"           # high resolution
)

```





### Figure 3: Heat Maps- Afghan Share(2020 vs 1996)

```{r}

## 1) Read Iran shapefile + data
iran <- sf::st_read(
  "Mapping/iranmap/irn_admbnda_adm1_unhcr_20190514.shp"
) %>%
  rename(Province = ADM1_EN)

sarshomari_1375 <- read_xlsx("Sarshomari_1375.xlsx")
LFS             <- read_dta("LFS.dta")

## 2) 1996 – make it PERCENT (Afghans / Total * 100)
sarshomari_1375 <- sarshomari_1375 %>%
  mutate(
    Afghans = as.numeric(Afghans),
    Total   = as.numeric(Total),
    Afghan_pct_1375 = 100 * Afghans / Total
  ) %>%
  select(Province, Afghan_pct_1375)

## 3) 1399 – LFS subset and province-level percent
LFS99 <- LFS %>% filter(year == 99)

lfs_1399 <- LFS99 %>%
  rename(Province = province_name,
         afghan_pct_1399=afghan_pct)

## 4) Merge both years to map
iran <- iran %>%
  left_join(sarshomari_1375, by = "Province") %>%
  left_join(lfs_1399,        by = "Province")

iran_border <- sf::st_union(iran)

## 5) Long format for faceting
iran_long <- iran %>%
  select(Province, Afghan_pct_1375, afghan_pct_1399, geometry) %>%
  pivot_longer(
    cols      = c(Afghan_pct_1375, afghan_pct_1399),
    names_to  = "year",
    values_to = "afghan_share"
  ) %>%
  mutate(
    year = dplyr::recode(
      year,
      "Afghan_pct_1375" = "Afghan Population Share,1996",
      "afghan_pct_1399" = "Afghan Population Share,2020"
    ),
    year = factor(
      year,
      levels = c("Afghan Population Share,1996",
                 "Afghan Population Share,2020")
    )
  )

## 6) Palette + common range
blue_pal  <- colorRampPalette(c("white", "#08519c"))(100)
val_range <- range(iran_long$afghan_share, na.rm = TRUE)

## 6.5) Correlation + significance stars (ONE value)
corr_data <- iran %>%
  st_drop_geometry() %>%
  select(Afghan_pct_1375, afghan_pct_1399) %>%
  na.omit()

corr_test <- cor.test(
  corr_data$Afghan_pct_1375,
  corr_data$afghan_pct_1399
)

corr_val <- unname(corr_test$estimate)
p_val    <- corr_test$p.value

stars <- {
  if (p_val < 0.001) {
    "***"
  } else if (p_val < 0.01) {
    "**"
  } else if (p_val < 0.05) {
    "*"
  } else {
    ""
  }
}

corr_label <- sprintf("Correlation (1996 vs 2020) = %.3f%s",
                      corr_val, stars)

## 7) Final two-panel map with ONE centered correlation caption
ggplot() +
  geom_sf(
    data  = iran_long,
    aes(fill = afghan_share),
    color = "grey70",
    size  = 0.3
  ) +
  geom_sf(
    data        = iran_border,
    fill        = NA,
    color       = "black",
    size        = 0.6,
    inherit.aes = FALSE
  ) +
  facet_wrap(~ year, ncol = 2) +
  scale_fill_gradientn(
    colours  = blue_pal,
    na.value = "#f0f0f0",
    limits   = val_range,
    name     = "Share (%)"
  ) +
  labs(caption = corr_label) +
  theme_void() +
  theme(
    legend.position   = "bottom",
    strip.text        = element_text(size = 11, face = "bold"),
    plot.margin       = margin(5, 5, 5, 5),
    plot.caption      = element_text(hjust = 0.5, vjust = 1,
                                     size = 10, face = "bold")
  )


ggsave(
  filename = "Afghan_Population_Share_1996_2020.png",
  plot     = last_plot(),   # saves the most recent ggplot
  width    = 10,            # inches
  height   = 6,
  dpi      = 300,
  bg       = "white"
)

```


### Figure 4: Male Share of Iranians, Afghans and the rest in 2023 (LFS)
```{r}

LFS402 <- read_dta("LFS_individuals2023.dta")

# 1. Prepare variables -----------------------------------------------------
LFS402 <- LFS402 %>%
  mutate(
    male = if_else(gender == 1, 1,
                   if_else(gender == 2, 0, NA_real_)),
    nat_cat = factor(
      nationality,
      levels = c(1, 2, 3),
      labels = c("Iranians", "Afghans", "Others")
    )
  )

# 2. Survey design ---------------------------------------------------------
des <- svydesign(ids = ~1, weights = ~IW_Yearly, data = LFS402)

# 3. Weighted male share + CI ---------------------------------------------
est <- svyby(~male, ~nat_cat, des, svymean, vartype = "se", na.rm = TRUE)

est <- est %>%
  mutate(
    mean_pct = male * 100,
    lower = (male - 1.96 * se) * 100,
    upper = (male + 1.96 * se) * 100,
    label_txt = sprintf("%.2f", male)
  )

# 4. Bar chart (Jordan-style greys) ---------------------------------------
ggplot(est, aes(x = nat_cat, y = mean_pct, fill = nat_cat)) +

  geom_col(width = 0.7, color = "black") +

  geom_errorbar(aes(ymin = lower, ymax = upper),
                width = 0.15, color = "red", linewidth = 0.7) +

  geom_text(aes(label = label_txt),
            vjust = -0.5, size = 4) +

  scale_fill_manual(
    values = c(
      "Iranians" = "#4D4D4D",   # dark grey
      "Afghans"  = "#808080",   # medium grey
      "Others"   = "#BFBFBF"    # light grey
    ),
    name = ""
  ) +

  labs(
    x = "",
    y = "Male (% of Population)"
  ) +

  theme_bw(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.major.x = element_blank()
  )

ggsave(
  filename = "male_share2023.png",
  plot     = last_plot(),
  width    = 6,
  height   = 4,
  dpi      = 300,
  bg       = "white"   # prevents black background
)
```



### Figure 5: Population Pyramid, LFS 2023

```{r}

# 1. Prep data -------------------------------------------------------------
LFS_pyr <- LFS402 %>%
  filter(nationality %in% c(1, 2)) %>%                      # 1=Iranians, 2=Afghans
  mutate(
    age_num = suppressWarnings(as.numeric(as.character(age))),
    wt      = suppressWarnings(as.numeric(as.character(IW_Yearly))),
    nat = factor(nationality,
                 levels = c(1, 2),
                 labels = c("Iranians", "Afghans")),
    sex = factor(gender,
                 levels = c(1, 2),
                 labels = c("Male", "Female")),
    age_group = cut(
      age_num,
      breaks = c(-Inf, 0, 4, 9, 14, 19, 24, 29, 34, 39,
                 44, 49, 54, 59, 64, 69, 74, 79, Inf),
      labels = c("<1", "1-4", "5-9", "10-14", "15-19",
                 "20-24", "25-29", "30-34", "35-39",
                 "40-44", "45-49", "50-54", "55-59",
                 "60-64", "65-69", "70-74", "75-79", "80+"),
      right = TRUE
    )
  ) %>%
  filter(!is.na(age_group), !is.na(sex), !is.na(nat), !is.na(wt))

# 2. Weighted totals (population in thousands) -----------------------------
pyr_df <- LFS_pyr %>%
  group_by(nat, sex, age_group) %>%
  summarise(pop = sum(wt, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    pop_thousands = pop / 1000,
    plot_value = ifelse(sex == "Male", -pop_thousands, pop_thousands)
  )

max_pop <- max(abs(pyr_df$plot_value), na.rm = TRUE)

ggplot(pyr_df, aes(x = age_group, y = plot_value, fill = sex)) +
  geom_col(width = 0.9, colour = "black") +
  coord_flip() +
  facet_wrap(~nat, nrow = 1, scales = "free_x") +
  scale_y_continuous(
    labels = abs,
    breaks = function(x) pretty(x, n = 5)   # <-- ensures visible axis labels per panel
  ) +
  scale_fill_manual(
    values = c("Male" = "#4D4D4D", "Female" = "#BFBFBF"),
    name = ""
  ) +
  labs(
    x = "",
    y = "Population in Thousands"
  ) +
  theme_bw(base_size = 12) +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_blank()
  )
ggsave(
  filename = "Population Pyramid2023.png",
  plot     = last_plot(),
  width    = 6,
  height   = 4,
  dpi      = 300,
  bg       = "white"   
)

```













